Exp1 - Opt w_max and {A,phi)

### 2018-01-26 voltagebudget/analysis/paper_figures.Rmd
analysis R code...working commit

>>>>

# Voltage budget timecourse

```{r}
vms <- read_csv("vm_comp_timecourse.csv")
```

```{r, fig.width=1.5, fig.height=1.3}
vms %>% 
  filter(t > 0.15, t < 0.35) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=vm)) +
  geom_ribbon(fill="blue", alpha=0.5) +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  labs(x="", y="Vm") +
  theme_classic() -> p1

vms %>% 
  filter(t > 0.15, t < 0.35) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=osc)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3, ymax=-50e-3),  fill=NA, color="black", alpha=0.01, size=.2) +
  # geom_hline(yintercept=-70e-3, color="black", size=1.5) +
  # geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), color="grey", alpha=0.5) +
  # geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3), fill=NA, color="grey", alpha=0.1) +
  labs(x="Times (s)", y="") +
  theme_classic() -> p2

vms %>% 
  filter(t > 0.23652 - 8e-3, t < 0.23652 + 2e-3 + 0.03333333 + 8e-3) %>%
  ggplot(aes(x=t, ymin=-70e-3, ymax=osc)) +
  geom_ribbon(fill="red", alpha=0.5) +
  geom_ribbon(aes(x=t, ymin=osc, ymax=comp), fill="purple", alpha=0.5) +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.5) +
  geom_hline(yintercept=-70e-3, color="black", linetype="dotted", size=0.5) +
  geom_rect(aes(xmin=0.23652 - 2e-3, xmax=0.23652, ymin=-70e-3, ymax=-50e-3), fill="grey", alpha=0.01) +
  geom_rect(aes(xmin=0.23652 + 2e-3, xmax=0.23652 + 2e-3 + 0.03333333, ymin=-70e-3, ymax=-50e-3),  fill="grey", alpha=0.01) +
  geom_rect(aes(xmin=0.23652 - 8e-3, xmax=0.23652 + 2e-3 + 0.03333333 + 8e-3, ymin=-70e-3, ymax=-50e-3),  fill=NA, color="black", alpha=0.01, size=.2) +
  labs(x="", y="") +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      # axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank()) -> p3

plot_grid <- rbind(c(1 , 1, NA), c(2, 2, 3))
grid.arrange(p1, p2, p3, layout_matrix=plot_grid)
```

# Voltage timecourses many neurons

```{r}
vms <- read_csv("vm_full_examples.csv")
vms <- gather(vms, "neuron", "vm", 2:21)
wins <- read_csv("vm_window_examples_d2_w2.csv")
wins <- gather(wins, "neuron", "vm", 2:21)
```

```{r, fig.width=1.5, fig.height=1}
vms %>% 
  filter(t > 0.15, t < 0.35) %>%
  ggplot(aes(x=t, y=vm, group=neuron)) +
  geom_line(color="black", alpha=0.3, size=0.2) +
  geom_line(data=wins, aes(x=t, y=vm), color="blue", alpha=0.5, size=1) +
  labs(x="Time (s)", y="Vm (mV)") +
  geom_hline(yintercept=-50e-3, color="black", linetype="dotted", size=0.25) +
  geom_hline(yintercept=-70e-3, color="black", size=2) +
  geom_vline(xintercept = 0.25719 + 2e-3, color="darkgreen", alpha=0.5, size=0.2) +
  geom_vline(xintercept = 0.25719 + 2e-3 +  0.03333333, color="darkgreen", alpha=0.5, size=0.2) +
  theme_classic()
```
```{r, fig.width=0.4, fig.height=0.8}
vms %>% 
  filter(t > 0.25, t < 0.27) %>%
  ggplot(aes(x=t, y=vm, group=neuron)) +
  geom_line(color="black", alpha=0.3, size=0.2) +
  geom_line(data=wins, aes(x=t, y=vm), color="blue", alpha=0.5, size=1) +
  labs(x="Time (s)", y="Vm (mV)") +
  geom_hline(yintercept=-50e-3, color="black", linetype="dashed", size=1) +
  geom_hline(yintercept=-70e-3, color="black", size=2) +
  theme(axis.line=element_blank(),
      axis.text.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks=element_blank(),
      axis.title.x=element_blank(),
      axis.title.y=element_blank(),
      legend.position="none",
      panel.background=element_blank(),
      panel.border=element_blank(),
      panel.grid.major=element_blank(),
      panel.grid.minor=element_blank(),
      plot.background=element_blank())
  # theme_classic()
```
